Evaluating Informative Hypotheses with Equality and Inequality Constraints:\\ A Tutorial Using the Bayes Factor via the Encompassing Prior Approach

### 2021-11-28 Documents/Paper/paper.Rnw
add doi

Data used for the illustrative application are part of a larger project on the socioemotional development of school-age children, which was approved by the Ethics Committee of the School of Psychology at the University of Padova (protocol \#[1838-2016]). All materials and data are available at [TODO].

@@

Externalizing problems according to attachment style are reported in Table~\ref{tab:table-cluster-ext}. More information about the sample, descriptive statistics, cluster analysis, and analysis of internalizing problems can be found in the Supplemental Material available online \url{https://claudiozandonella.github.io/Attachment/}. All materials and data are available at [TODO].

>>>>

Data used for the illustrative application are part of a larger project on the social-emotional development of school-age children, which was approved by the Ethics Committee of the School of Psychology at the University of Padova (protocol \#[1838-2016]). All materials and data are available at \url{10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}.

@@

Externalizing problems according to attachment style are reported in Table~\ref{tab:table-cluster-ext}. More information about the sample, descriptive statistics, cluster analysis, and analysis of internalizing problems can be found in the Supplemental Material available online \url{https://claudiozandonella.github.io/Attachment/}. All materials and data are available at \url{10.17605/OSF.IO/JKMDF}, GitHub repository \url{https://github.com/ClaudioZandonella/Attachment}.
